No time for dead time - Use the Fourier amplitude differences to normalize dead time-affected periodograms

### 2017-11-06 paper/deadtime.tex
Various improvements to data analysis section

\subsection{Cyg X-1 \nustar dataset}
We downloaded the observation directory of \nustar ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package (Bachetti et al., ASCL identifier requested).
Starting from the standard cleaned science event files distributed by HEASARC, we applied a barycenter correction using the FTOOL \texttt{barycorr} shipped with HEASOFT 6.21 with the clock correction file n. 71 from the \nustar CALDB.
We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.
We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and produced light curves with photons from 3 to 79 keV%
\footnote{This procedure uses the scripts \texttt{HENreadfile}, \texttt{HENcalibrate} and \texttt{HENlcurve}, as described at\\ \href{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}}.

@@

\begin{eqnarray}
A_{xj} &=& A_{xsj} + A_{xdj} + A_{xnj} \nonumber \\
B_{xj} &=& B_{xsj} + A_{xdj} + B_{xnj} \, ,
\end{eqnarray}

>>>>

\subsection{Cyg X-1 \nustar dataset}
We tested the method also on real data of several bright sources observed by \nustar.
As an example, we report here one such test done on \nustar data of the black hole binary Cyg~X-1 together with the steps to reproduce our analysis, using the linked Jupyter notebook if needed.
We downloaded the observation directory of \nustar ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package (Bachetti et al., ASCL identifier requested). 
Equivalently, this download can be done using the online tools provided by HEASARC (e.g. \texttt{xamin}).
Starting from the standard cleaned science event files distributed by HEASARC, we applied a barycenter correction using the FTOOL \texttt{barycorr} shipped with HEASOFT 6.21 with the clock correction file n. 71 from the \nustar CALDB.
We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.%
\footnote{To use the method on different sources, it is sufficient to download a different ObsID and change the region file containing the position of the source}.
We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and produced light curves with photons from 3 to 79 keV and binned with uniform time bins of 1/4096$\sim2.44\cdot10^{-4}$\,sec%
\footnote{This procedure uses the scripts \texttt{HENreadfile}, \texttt{HENcalibrate} and \texttt{HENlcurve}, as described at\\ \href{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}}.

@@

\begin{eqnarray}
A_{xj} &=& A_{xsj} + A_{xdj} + A_{xnj} \nonumber \\
B_{xj} &=& B_{xsj} + B_{xdj} + B_{xnj} \, ,
\end{eqnarray}
